\cvsection{Experience}
\begin{cventries}
  \cventry
    {Software Engineer(Cloud and Big Data Analysis)}
    {Hsbc software development India}
    {Pune,India}
    {July. 2016 - Present}
    {
      \begin{cvitems}
        \item {Was Topper in the 3 months Training Program(Android,Data Analytics,Cloud Computing ,IT Security,Agile ) at Infosys Mysore.}
        \item {Worked on Java,Spring,Dojo for internal Employee Management Software}
        \item {Member of the innovation Lap b Working on various POC like chat bots,Document Classification using Tensor Flow and machine Learning}
        \item {
        Part of Google Cloud Platform working on various cloud tools for the Company's Data Analytics projects.
        }
        \item{
        Part of the Blockchain team working on migrating projects to blockchain like ProxyVoting.
        }
      \end{cvitems}
    }
  \cventry
    {Intern Technology}
    {Proptiger(Makaan,Housing)}
    {Gurgaon}
    {Jan. 2016 - Jul. 2016}
    {
      \begin{cvitems}
        \item {Worked with the Backend API team developing API that are used by makaan.com using Java,Spring and Hibernate.
Also worked on various Like POC for Automation of Listing
POC for SMS analysis(NLP) and Notification Management System}
        \item {Gave Talk about SMS Analysis in the internal Tech Talk event for company employees}
      \end{cvitems}
    }
  \cventry
    {Worked on various Projects during college}
    {Undergraduate Projects,Thapar University}
    {Patiala,Punjab}
    {July. 2012 - July. 2016}
    {
      \begin{cvitems}
        \item {Automatic Hostel Allotment,Used by the college during counseling,(Awarded Departmental Best Project,Awarded Scholarship and \textbf{Best Project 2015} by Ch. Bhagwan Singh Nasa Parvati Nasa Charitable Trust)(PHP,Ajax,Javascript)}
        \item {Classification of Tweets (Naïve bayes Algorithm on Mahout in Hadoop)}
        \item {\textbf{Assignment Submission Portal},Hosted in the internal server and used by teacher for checking assignments(PHP,Ajax,Javascript)}
        \item{\textbf{Hostel Room Booking},used by students in Hostel for booking rooms every semester (PHP,Ajax ,Javascript)}
        \item{Twitter Sentiment Analysis \textbf{Research Paper}(Top 5 Projects of college)}
      \end{cvitems} 
    }
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
\end{cventries}
